---
title: "Dulce Final Project"
author: "Dulce Wilkinson"
date: "December 8, 2020"
output: html_document
---

```{r}
#Use point and click with menus to import data. 
```
#Rename data so it's easier to work with
```{r}
dat <- read_excel("Dulce Final Project Data.xlsx")
```

#Two Data Cleaning Techniques. I reverse coded two variables. 
```{r}
library(car)
cesd8r<-dat$cesd8<- recode(dat$cesd8, '1=4;2=3;3=2;4=1')
cesd12r<-dat$cesd12<- recode(dat$cesd12, '1=4;2=3;3=2;4=1')
```

#Analyses. I created a data frame of my variables of interest, so that I could generate a correlation matrix. I then conducted linear regressions between affective tone and psychological outcomes. 

```{r}
library(Hmisc)
datCor<-cbind.data.frame(dat$meimExplore, dat$meimBelong, dat$cesd, dat$energy, dat$emotiolWellBeing, dat$swl, dat$Redemption, dat$Contamition, dat$Tone)

datCorMat <- rcorr(as.matrix(datCor))
as.data.frame(datCorMat$P)
as.data.frame(datCorMat$r)
```

#Correlation matrix with p values.
```{r}
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
flattenCorrMatrix(datCorMat$r, datCorMat$P)
```

#Linear Regressions: Affective Tone predicting ethnic racial identity and psychological health variables. 

#Affective tone & Redemption -> meimBelong
```{r}
dat$zMeimBelong <- scale(dat$meimBelong)
lmBelong<- lm(zMeimBelong~Redemption, data=dat)
summary(lmBelong)

lmBelong2<- lm(zMeimBelong~Tone, data=dat)
summary(lmBelong2)
```

#Affective tone & Redemption -> meimExplore
```{r}
dat$zMeimExplore <- scale(dat$meimExplore)
lmExplore<- lm(zMeimExplore~Redemption, data=dat)
summary(lmBelong)

lmExplore2<- lm(zMeimExplore~Tone, data=dat)
summary(lmBelong2)
```

#Affective tone & Redemption -> cesd
```{r}
dat$zCesd <- scale(dat$cesd)
lmCesd<- lm(zCesd~Redemption, data=dat)
summary(lmCesd)

lmCesd2<- lm(zCesd~Tone, data=dat)
summary(lmCesd2)
```

#Affective tone & Redemption -> swl
```{r}

dat$zSwl <- scale(dat$swl)
lmSwl<- lm(zSwl~Redemption, data=dat)
summary(lmSwl)


lmSwl2<-lm(zSwl~ Tone, data=dat)
summary(lmSwl2)
```

#Affective tone & Redemption -> energy
```{r}
dat$zEnergy <- scale(dat$energy)
lmEnergy<-lm(energy~ Redemption, data=dat)
summary(lmEnergy)

lmEnergy2<-lm(energy ~ Tone, data=dat)
summary(lmEnergy2)
```

#Here, I examined mean differences in redemption and contamination based on ethnicity
```{r}
t.test(Redemption~T1_Ethnicity_A, data=dat, var.equal=TRUE)
```

```{r}
t.test(Contamition~T1_Ethnicity_A, data=dat, var.equal=TRUE)
```

#One Graph. I created a frequency bar graph to depict the frequency of redemptive themes between Asian American and Latinx participants. 

```{r}
cTab <- table(dat$Redemption, dat$T1_Ethnicity_A)
barplot(cTab, beside=TRUE, legend.text=rownames(cTab), ylab="absolute frequency")
```

```{r}
library(reshape2)
library(ggplot2)
library(dplyr)
data_m <- melt(cTab, varnames = c("Red", "Eth"), id.vars = "Red")

ggplot(data_m %>% group_by(Red) %>% 
           mutate(perc = round(value/sum(value),2)), 
       aes(x = as.factor(Red), y = perc, 
           fill = as.factor(Eth), cumulative = TRUE)) +
    geom_col() +
    geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5))
```



